MIRSVM: Multi-Instance Support Vector Machine with Bag Representatives

### 2017-06-16 ArticleRevision/article/article.tex
Dataset table, run-time, ignore *.m~
> added explanation of run-time (train+test)
> ignore m~ files
> re-ordered dataset table to be in order of increasing bag size

\begin{table}[t!]
\caption{Datasets used for the experiments in~\ref{subsec:results}}
\small
\label{tab:Dataset}
\begin{tabularx}{\textwidth}{l@{\extracolsep{\fill}}ccccc}
\hline\noalign{\smallskip}
Dataset & Attributes & Positive Bags & Negative Bags & Total & Instances \\
\noalign{\smallskip}\hline\noalign{\smallskip}
Suramin 			& 20 	& 7 	& 4 	& 11 	& 2378 	\\
EastWest 			& 24 	& 10 	& 10 	& 20 	& 213 	\\
WestEast 			& 24 	& 10 	& 10 	& 20 	& 213 	\\
Musk1 				& 166 	& 47 	& 45 	& 92 	& 476 	\\
Musk2 				& 166 	& 39 	& 63 	& 102 	& 6598 	\\
Webmining			& 5863	& 17	& 58	& 75	& 2212	\\
TRX 				& 8 	& 25 	& 193 	& 168 	& 26611 \\
Mutagenesis-Atoms 	& 10 	& 125 	& 63 	& 188 	& 1618 	\\
Mutagenesis-Bonds 	& 16 	& 125 	& 63 	& 188 	& 3995 	\\
Mutagenesis-Chains 	& 24 	& 125 	& 63 	& 188 	& 5349 	\\
Tiger 				& 230 	& 100 	& 100 	& 200 	& 1391 	\\
Elephant 			& 230 	& 100 	& 100 	& 200 	& 1220 	\\
Fox 				& 230 	& 100 	& 100 	& 200 	& 1320 	\\
Component			& 22	& 423	& 2707	& 3130	& 36894	\\
Function			& 202	& 443	& 4799	& 5242	& 55536	\\
\noalign{\smallskip}\hline
\end{tabularx}
\end{table}

@@

\subsection{Results \& Statistical Analysis}\label{subsec:results}
The classification performance was measured using five metrics: Accuracy~\eqref{eq:accuracy}, Precision \eqref{eq:precision}, Recall~\eqref{eq:recall}, Cohen's kappa rate~\eqref{eq:kappa}, and Area under ROC curve (AUC)~\eqref{eq:auc}. Accuracy can be misleading when classes are imbalanced, as is the case with the \textit{component} and \textit{function} datasets, which have six and ten times as many negative instances than positive, respectively. Cohen's Kappa Rate and the AUC measures are used as complementary measures in order to evaluate the algorithms comprehensively~\citep{Bendavid2008}. Cohen's kappa rate, shown in Equation~\eqref{eq:kappa}, evaluates classifier merit according to the class distribution and ranges between -1 (full disagreement), 0 (random classification), and 1 (full agreement). The AUC metric highlights the trade-off between the true positive rate, or recall, and the false positive rate, as shown in Equation~\eqref{eq:auc}. The values of the true positive (TP), true negative (TN), false positive (FP), and false negative samples (FN) were first collected for each of the classifiers, then the metrics were computed using the equations shown in~\eqref{eq:metrics} on the $n^\prime$ bags of the test data. The run times of each algorithm are also reported to analyze the usability and speed of each of the algorithms across differently sized datasets.

>>>>

\begin{table}[t!]
\caption{Datasets used for the experiments in~\ref{subsec:results}}
\small
\label{tab:Dataset}
\begin{tabularx}{\textwidth}{l@{\extracolsep{\fill}}ccccc}
\hline\noalign{\smallskip}
Dataset & Attributes & Positive Bags & Negative Bags & Total & Instances \\
\noalign{\smallskip}\hline\noalign{\smallskip}
Suramin 			& 20 	& 7 	& 4 	& 11 	& 2378 	\\
EastWest 			& 24 	& 10 	& 10 	& 20 	& 213 	\\
WestEast 			& 24 	& 10 	& 10 	& 20 	& 213 	\\
Webmining			& 5863	& 17	& 58	& 75	& 2212	\\
Musk1 				& 166 	& 47 	& 45 	& 92 	& 476 	\\
Musk2 				& 166 	& 39 	& 63 	& 102 	& 6598 	\\
TRX 				& 8 	& 25 	& 193 	& 168 	& 26611 \\
Mutagenesis-Atoms 	& 10 	& 125 	& 63 	& 188 	& 1618 	\\
Mutagenesis-Bonds 	& 16 	& 125 	& 63 	& 188 	& 3995 	\\
Mutagenesis-Chains 	& 24 	& 125 	& 63 	& 188 	& 5349 	\\
Tiger 				& 230 	& 100 	& 100 	& 200 	& 1391 	\\
Elephant 			& 230 	& 100 	& 100 	& 200 	& 1220 	\\
Fox 				& 230 	& 100 	& 100 	& 200 	& 1320 	\\
Component			& 22	& 423	& 2707	& 3130	& 36894	\\
Function			& 202	& 443	& 4799	& 5242	& 55536	\\
\noalign{\smallskip}\hline
\end{tabularx}
\end{table}

@@

\subsection{Results \& Statistical Analysis}\label{subsec:results}
The classification performance was measured using five metrics: Accuracy~\eqref{eq:accuracy}, Precision \eqref{eq:precision}, Recall~\eqref{eq:recall}, Cohen's kappa rate~\eqref{eq:kappa}, and Area under ROC curve (AUC)~\eqref{eq:auc}. Accuracy can be misleading when classes are imbalanced, as is the case with the \textit{component} and \textit{function} datasets, which have six and ten times as many negative instances than positive, respectively. Cohen's Kappa Rate and the AUC measures are used as complementary measures in order to evaluate the algorithms comprehensively~\citep{Bendavid2008}. Cohen's kappa rate, shown in Equation~\eqref{eq:kappa}, evaluates classifier merit according to the class distribution and ranges between -1 (full disagreement), 0 (random classification), and 1 (full agreement). The AUC metric highlights the trade-off between the true positive rate, or recall, and the false positive rate, as shown in Equation~\eqref{eq:auc}. The values of the true positive (TP), true negative (TN), false positive (FP), and false negative samples (FN) were first collected for each of the classifiers, then the metrics were computed using the equations shown in~\eqref{eq:metrics} on the $n^\prime$ bags of the test data. The run times (training and testing times) of each algorithm are also reported to analyze the usability and speed of each of the algorithms across differently sized datasets.
